Automatically generated NE tagged corpora for English and Hungarian

### 2012-06-30 paper/jeju_presentation.tex
"Creating the English Corpus" part done.

\documentclass[utf8x]{beamer}

@@

\subsection*{Motivation}
\begin{frame}{Motivation}
  \begin{itemize}
  \vitem Our goal is to create a large NE annotated corpus, automatically
        generated from WP articles.
  \vitem Our method is similar to Nothman et al. (2008)
  \vitem The process consists of four steps:
    \begin{enumerate}
    \vitem Classify WP articles into entity classes.
    \vitem Parse WP and split articles into sentences.
    \vitem Label named entities in the text.
    \vitem Select the sentences for inclusion in the corpus.
    \end{enumerate}
  \end{itemize}
\end{frame}

\subsection{Articles to Entities}
\begin{frame}{Problem Statement}
  In many real world applications the problem is to predict outputs with a nontrivial structure given some inputs.
  \vfill
  Example: \textit{\small It was love at first sight.}
  \vfill
\end{frame}

\subsection{}
\subsection{}
\subsection{}

>>>>

\documentclass[utf8x,t]{beamer}

@@

\subsection*{Motivation}
\begin{frame}{Motivation}
  \begin{itemize}
  \vitem Our goal is to create a large NE annotated corpus, automatically
        generated from WP articles.
  \vitem Our method is similar to Nothman et al. (2008)
  \vitem The process consists of four steps:
    \begin{enumerate}
    \vitem Classify WP articles into entity classes.
    \vitem \textit{Parse WP and split articles into sentences.}
    \vitem Label named entities in the text.
    \vitem Select the sentences for inclusion in the corpus.
    \end{enumerate}
  \end{itemize}
\end{frame}

\subsection{Articles to Entities}
\begin{frame}{Articles to Entities}
  Our method is based on thinking of WP articles as NEs.
  \begin{itemize}
  \vitem Usual approach: semi-supervised learning (infoboxes, first sentence)
  \vitem Our approach: create entity list from DBpedia
    \begin{itemize}
    \vitem OWL ontology with 320 classes
    \vitem We take the most specific class
    \vitem Manual mapping to CoNLL categories that exploits inheritence
    \end{itemize}
  \vitem Decreased coverage, increased precision
  \end{itemize}
\end{frame}

\subsection{Named Entity Tagging}
\begin{frame}{Named Entity Tagging}
  The entity list from DBpedia is used for NE tagging.
  \begin{itemize}
  \vitem Entity identification:
    \begin{itemize}
    \vitem Look up linked pages in the entity list
    \vitem References to the current page, if in the list
    \end{itemize}
  \vitem NE tagging: from the DBpedia - CoNLL category mapping
  \vitem Exceptions:
    \begin{itemize}
    \vitem Not entities: common nouns, date expressions, etc.
    \vitem Unmarked entities: link to already identified entities
    \vitem Special cases: derived words, first word in a sentence, etc.
    \end{itemize}
  \end{itemize}
\end{frame}

\subsection{Sentence Filtering}
\begin{frame}{Sentence Filtering}
  We only include fully tagged sentences in the corpus.
  \begin{itemize}
  \vitem Sentences that contain unknown links / uppercase words
  \vitem To filter incomplete sentences:
    \begin{itemize}
    \vitem Sentences without an EOS punctuation mark
    \vitem Sentences without a predicate (verb)
    \end{itemize}
  \end{itemize}
  \vfill
\end{frame}
